Future Directions

### 2021-03-09 manuscripts/laplacian_smoothing/arXiv/minimax_optimal_laplacian_smoothing.tex
Updated the AISTATS camera-ready version.

We adopt the standard nonparametric regression setup, where we observe samples $(X_1,Y_1),\ldots,(X_n,Y_n)$ that are i.i.d.\ draws from the model 
\begin{equation}
\label{eqn:signal_plus_noise_model}
Y_i = f_0(X_i) + \varepsilon_i, \quad \epsilon_i \sim N(0,1), 
\end{equation}
where $\varepsilon_i$ is independent of $X_i$. Our goal is to perform statistical inference on the unknown regression function $f_0$, by which we mean either \emph{estimating} $f_0$ or \emph{testing} whether $f_0 = 0$, i.e., whether there is any signal present.

@@

To summarize: for $d = 1,2,$ or $3$, with high probability, the Laplacian smoothing estimator \smash{$\wh{f}$} has in-sample mean squared error that is within a constant factor of the minimax error. Some remarks:
\begin{itemize}
	\item The first-order Sobolev space $H^1(\Xset)$ does not continuously embed into $C^0(\Xset)$ when $d>1$ (in general, the $k$th order space $H^k(\Xset)$ does not continuously embed into $C^0(\Xset)$ except if $2k>d$). For this reason, one really cannot speak of pointwise evaluation of a Sobolev function $f_0 \in H^1(\Xset)$ when $d>1$ (as we do in Theorem~\ref{thm:laplacian_smoothing_estimation1} by defining our target of estimation to be $f_0(X_i)$, $i=1,\ldots,n$). We can resolve this by appealing to what are known as \emph{Lebesgue points}, as explained in Appendix~\ref{app:preliminaries}.
	% RJT: Alden, please add a section to the supplement to explain this part.
	% AJG: Added.
	\item The assumption $M \leq n^{1/d}$ ensures that the upper bound provided in the theorem is meaningful (i.e., ensures it is of at most a constant order).
	\item The lower bound on $r$ imposed in condition \ref{asmp:ls_kernel_radius_estimation} is compatible with practice, where by far the most common choice of radius is the connectivity threshold \smash{$r \asymp (\log(n)/n)^{1/d}$}, which makes \smash{$G_{n,r}$} as sparse as possible while still being connected, for maximum computational efficiency. The upper bound may seem a bit more mysterious---we need it for technical reasons to ensure that \smash{$\wh{f}$} does not overfit, but we note that as a practical matter one rarely chooses $r$ to be so large anyway.
	\item It is possible to extend \smash{$\wh{f}$} to be defined on all of $\Xset$ and then evaluate the error of such an extension (as measured against $f_0$) in $\Leb^2(\Xset)$ norm. When \smash{$\wh{f}$} and $f_0$ are suitably smooth, tools from empirical process theory (see e.g., Chapter 14 of \citet{wainwright2019}) or approximation theory (e.g., Section 15.5 of \citet{johnstone2011}) guarantee that the $\Leb^2(\Xset)$ error is not too much greater than its in-sample counterpart. In fact, as shown in Appendix~\ref{sec:graph_sobolev_seminorm}, if $f_0$ is Lipschitz smooth and we extend \smash{$\wh{f}$} to be piecewise constant over the Voronoi tesselation induced by $X_1,\ldots,X_n$, then the out-of-sample error \smash{$\|\wh{f}-f_0\|_{\Leb^2(\Xset)}$} is within a negligible factor of the in-sample error \smash{$\|\wh{f}-f_0\|_n$}. We leave analysis of the Sobolev case to future work.
	\item When $f_0$ is Lipschitz smooth, we can also replace the factor of $\delta$ in the high probability bound by a factor of $\delta^2/n$, which is always smaller than $\delta$ when $\delta \in (0,1)$.\\
	%\sbcomment{Too mysterious a comment. Why is this sharper?} \\
	%\agcomment{Attempted to resolve.} 
\end{itemize}

@@

We emphasize that little about $\Xset$ needs be known for Theorems~\ref{thm:laplacian_smoothing_estimation_manifold} and \ref{thm:laplacian_smoothing_testing_manifold} to hold. Indeed, all that is needed is the intrinsic dimension $m$, to properly tune $r$ and $\rho$ (from a theoretical point of view), and otherwise \smash{$\wh{f}$} and \smash{$\wh{\varphi}$} are computed without regard to $\Xset$. In contrast, the penalty in \eqref{eqn:thin_plate_spline} would have to be specially tailored to work in this setting, revealing another advantage of the discrete approach over the variational one.

@@

\subsection*{Acknowledgements}
AG and RJT were supported by ONR grant N00014-20-1-2787. AG and SB were supported by NSF grants DMS-1713003 and CCF-1763734.

\bibliographystyle{unsrtnat}
\bibliography{../../../graph_regression_bibliography}

>>>>

We adopt the standard nonparametric regression setup, where we observe samples $(X_1,Y_1),\ldots,(X_n,Y_n)$ that are i.i.d.\ draws from the model 
\begin{equation}
\label{eqn:signal_plus_noise_model}
Y_i = f_0(X_i) + \varepsilon_i, \quad \varepsilon_i \sim N(0,1), 
\end{equation}
where $\varepsilon_i$ is independent of $X_i$. Our goal is to perform statistical inference on the unknown regression function $f_0$, by which we mean either \emph{estimating} $f_0$ or \emph{testing} whether $f_0 = 0$, i.e., whether there is any signal present.

@@

To summarize: for $d = 1,2,$ or $3$, with high probability, the Laplacian smoothing estimator \smash{$\wh{f}$} has in-sample mean squared error that is within a constant factor of the minimax error. Some remarks:
\begin{itemize}
	\item The first-order Sobolev space $H^1(\Xset)$ does not continuously embed into $C^0(\Xset)$ when $d>1$ (in general, the $k$th order space $H^k(\Xset)$ does not continuously embed into $C^0(\Xset)$ except if $2k>d$). For this reason, one really cannot speak of pointwise evaluation of a Sobolev function $f_0 \in H^1(\Xset)$ when $d>1$ (as we do in Theorem~\ref{thm:laplacian_smoothing_estimation1} by defining our target of estimation to be $f_0(X_i)$, $i=1,\ldots,n$). We can resolve this by appealing to what are known as \emph{Lebesgue points}, as explained in Appendix~\ref{app:preliminaries}.
	% RJT: Alden, please add a section to the supplement to explain this part.
	% AJG: Added.
	\item The assumption $M \leq n^{1/d}$ ensures that the upper bound provided in the theorem is meaningful (i.e., ensures it is of at most a constant order).
	\item The lower bound on $r$ imposed in condition \ref{asmp:ls_kernel_radius_estimation} is compatible with practice, where by far the most common choice of radius is the connectivity threshold \smash{$r \asymp (\log(n)/n)^{1/d}$}, which makes \smash{$G_{n,r}$} as sparse as possible while still being connected, for maximum computational efficiency. The upper bound may seem a bit more mysterious---we need it for technical reasons to ensure that \smash{$\wh{f}$} does not overfit, but we note that as a practical matter one rarely chooses $r$ to be so large anyway.
	\item It is possible to extend \smash{$\wh{f}$} to be defined on all of $\Xset$ and then evaluate the error of such an extension (as measured against $f_0$) in $\Leb^2(\Xset)$ norm. When \smash{$\wh{f}$} and $f_0$ are suitably smooth, tools from empirical process theory (see e.g., Chapter 14 of \citet{wainwright2019}) or approximation theory (e.g., Section 15.5 of \citet{johnstone2011}) guarantee that the $\Leb^2(\Xset)$ error is not too much greater than its in-sample counterpart. In fact, as shown in Appendix~\ref{sec:graph_sobolev_seminorm}, if $f_0$ is Lipschitz smooth and we extend \smash{$\wh{f}$} to be piecewise constant over the Voronoi tessellation induced by $X_1,\ldots,X_n$, then the out-of-sample error \smash{$\|\wh{f}-f_0\|_{\Leb^2(\Xset)}$} is within a negligible factor of the in-sample error \smash{$\|\wh{f}-f_0\|_n$}. We leave analysis of the Sobolev case to future work.
	\item When $f_0$ is Lipschitz smooth, we can also replace the factor of $\delta$ in the high probability bound by a factor of $\delta^2/n$, which is always smaller than $\delta$ when $\delta \in (0,1)$.
	%\sbcomment{Too mysterious a comment. Why is this sharper?} \\
	%\agcomment{Attempted to resolve.} 
\end{itemize}

@@

We emphasize that little about $\Xset$ need be known for Theorems~\ref{thm:laplacian_smoothing_estimation_manifold} and \ref{thm:laplacian_smoothing_testing_manifold} to hold. Indeed, all that is needed is the intrinsic dimension $m$, to properly tune $r$ and $\rho$ (from a theoretical point of view), and otherwise \smash{$\wh{f}$} and \smash{$\wh{\varphi}$} are computed without regard to $\Xset$. In contrast, the penalty in \eqref{eqn:thin_plate_spline} would have to be specially tailored to work in this setting, revealing another advantage of the discrete approach over the variational one.

@@

\subsection*{Acknowledgments}
AG and RJT were supported by ONR grant N00014-20-1-2787. AG and SB were supported by NSF grants DMS-1713003 and CCF-1763734.

\bibliographystyle{plainnat}
\bibliography{../../../graph_regression_bibliography}
